---
title: "BTL"
output: html_document
date: "2024-03-29"
---

1.Data Reading and Data Cleaning

- Loading the libraries used in the assignment

```{r}
library('dplyr')
library('magrittr')
library('GGally')
library('corrplot')
library('MASS')
library('car')
```

- Read the dataset All_GPUs.csv and import it into the dataframe GPU_data
```{r}
GPU_data <- read.csv("All_GPUs.csv")
summary(GPU_data)
```
- Extracting features Manufacturer, Process, Max_Power, Memory_Speed, Memory_Bus, Pixel_Rate, Texture_Rate and Memory_Bandwidth from GPU_data and stores them in new dataframe new_data
```{r}
new_data <- GPU_data %>% dplyr::select("Manufacturer","Process","Max_Power","Memory_Speed","Memory_Bus","Memory","Core_Speed","Memory_Bandwidth")
str(new_data)
```
- Eliminate the unit of Process 
```{r}
new_data$Process <- as.numeric(sub("nm", "", new_data$Process))
```

- Eliminate the unit of Max_Power
```{r}
new_data$Max_Power <- as.numeric(sub("Watts", "" , new_data$Max_Power))
```

- Eliminate the unit of Memory_Speed
```{r}
new_data$Memory_Speed <- as.numeric(sub("MHz", "", new_data$Memory_Speed))
```

- Eliminate the unit of Memory_Bus
```{r}
new_data$Memory_Bus <- as.numeric(sub("Bit", "", new_data$Memory_Bus))
```

- Eliminate the unit of Memory
```{r}
new_data$Memory <- as.numeric(sub("MB", "", new_data$Memory))
```

- Eliminate the unit of Core_Speed
```{r}
new_data$Core_Speed <- as.numeric(sub("MHz", "", new_data$Core_Speed))
```
- Eliminate the unit of Memory_Bandwidth
```{r}
new_data$Memory_Bandwidth <- as.numeric(sub("GB/sec", "", new_data$Memory_Bandwidth))
```

- Check for new_data 's NA and negatives

```{r}
colSums(is.na(new_data))
```
- Eliminate NA:
```{r}
new_data <- na.omit(new_data)
```

3. Data Visualization: 
- Sum up basic information about a portion of numeric variables in the data set
```{r}
summary(new_data[,c(2:8)])
```
- Overview of the relation between each pair of variable
```{r}
ggpairs(new_data[,c(2:8)])
```

- Utilizing Histogram and Boxplot
```{r}
dtplot <- function (new_data , col , na.rm = TRUE) { # display the 2 plots side by side
  hist ( new_data [[ col ]] ,
  main = paste ( " Histogram of " , col ) ,
  xlab = col,cex.main=1.2,
  cex.lab=1.2)
  boxplot ( new_data [[ col ]] ,
  main = paste ( " Boxplot of " , col ),
  horizontal = T ,
  xlab = col ,
  ylab = "" ,
  las = 3,
  cex.main=1.2,
  cex.lab=1.2)
}
```

- Plot each variable
```{r}
plot_all <- function(new_data, na.rm = TRUE) {
  par(mfrow = c(1, 4))  
  col_names <- names(new_data[,c(2:8)])
  for (col in col_names) {
    dtplot(new_data,col,na.rm)
  }
}
plot_all(new_data)
```
- Heatmap
```{r} 
correlation_matrix <- cor(new_data[,c(2:8)])
corrplot(correlation_matrix, method = "square", addCoef.col= "yellow",tl.col="black",tl.cex=1.1)
```

4. Multiple Linear Regression
In this section, we will build a multiple linear regression model with Memory_Bandwidth as the dependent variable, and Process, Max_Power, Memory_Speed, Memory_Bus, Memory, Pixel_Rate, Texture_Rate as the independent variables. Our objective is to develop a predictive model that can accurately estimates Memory_Bandwidth based on other factors. 


- Fitting the model:

```{r}
model1 <- lm(formula = Memory_Bandwidth ~ Core_Speed + Memory + Memory_Bus + Memory_Speed + Max_Power + Process, data = new_data)
summary(model1)
```
- Create a new model remove the Memory_Speed variable: 

```{r}
model2 <- lm(formula = Memory_Bandwidth ~ Core_Speed + Memory + Memory_Bus + Max_Power + Process, data = new_data)
summary(model2)
```

- Multicolinearity check:

We conducted a VIF analysis in model2: 

```{r}
print(vif(model2))
```

- Factorial ANOVA
Consider the factorial ANOVA test for model1: 
```{r}
Anova(model1, type=2)
```
Test the factorial ANOVA for model2:

```{r}
Anova(model2, type=2)
```
- Using ANOVA to compare 2 models:

```{r}
anova(model1, model2)
```

5. Residual plots

```{r}
plot(model2)
```
